Effect of quality-adjusted production function inputs

### 2015-05-18 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Now creating an AllCoeffs data frame.

  models <- list()
  for(country in countries){
    for (flavor in flavors){
      fnoE <- keep_summands(formulas[[country]][[flavor]], -3) # Drop the energy term
      fwithE <- formulas[[country]][[flavor]]
      # CD models
      models[[country]][[flavor]][["noE"]][["CD"]]   <- cdModel(fnoE, data = historicalData[[country]])
      models[[country]][[flavor]][["withE"]][["CD"]] <- cdModel(fwithE, data = historicalData[[country]])
      # CES models
      models[[country]][[flavor]][["noE"]][["CES"]][["kl"]] <- cesModel(fnoE, data = historicalData[[country]], nest=c(1,2))
      models[[country]][[flavor]][["withE"]][["CES"]] <- 
        lapply(nests, function(nest){
          cesModel(formula=fwithE, data=historicalData[[country]], nest=nest)
        })
    }      
  }
  # Save models to disk.
  save(models, file=fileName)
}
@

<<Fitted_and_Residuals>>=
fitted_and_resid_data <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), function(mod, id){
  df <- select(mod$data, Year, iGDP, Country)
  # Trim fitted to be same length as df to eliminate problems with possible NAs at end of fitted
  df$fitted <- yhat(mod)[c(1:length(df$Year))]
  df$Residuals <- resid(mod)[c(1:length(df$Year))]
  # Parse the id to find out whether this is quality-adjusted data
  id_list <- strsplit(id, split = "[.]")[[1]]
  if (id_list[[2]] == "unadjusted"){
    df$flavor <- "Unadjusted"
  } else if (id_list[[2]] == "adjusted"){
    df$flavor <- "Quality-adjusted"
  } else {
    stop("Unknown adjustment.")
  }
  if (id_list[[3]] == "noE"){
    df$energy <- "Without energy"
  } else if (id_list[[3]] == "withE"){
    df$energy <- "With energy"
  } else {
    stop("Unknown energy.")
  }
  df$model <- id_list[[4]]
  df$nest <- if (length(id_list) > 4) id_list[[5]] else NA
  return(df)  
}) %>% do.call(rbind, .)

>>>>

  models <- list()
  for(country in countries){
    for (flavor in flavors){
      fnoE <- keep_summands(formulas[[country]][[flavor]], -3) # Drop the energy term
      fwithE <- formulas[[country]][[flavor]]
      # CD models
      models[[country]][[flavor]][["noE"]][["CD"]]   <- cdModel(fnoE, data = historicalData[[country]])
      models[[country]][[flavor]][["withE"]][["CD"]] <- cdModel(fwithE, data = historicalData[[country]])
      # CES models
      models[[country]][[flavor]][["noE"]][["CES"]][["kl"]] <- cesModel(fnoE, data = historicalData[[country]], nest=c(1,2))
      models[[country]][[flavor]][["withE"]][["CES"]] <- 
        lapply(nests, function(nest){
          cesModel(formula=fwithE, data=historicalData[[country]], nest=nest)
        })
    }      
  }
  # Save models to disk.
  save(models, file=fileName)
}
# Put all the coefficients into a data frame
AllCoeffs <- leaf_apply(models, class = c("CDEmodel", "cesModel", "LINEXmodel"), f = function(mod, id){
  # Parse the id to find out whether this is quality-adjusted data, etc.
  id_list <- strsplit(id, split = "[.]")[[1]]
  Country <- id_list[[1]]
  flavor <- id_list[[2]]
  energy <- id_list[[3]]
  model <- id_list[[4]]
  nest <- if(length(id_list) > 4) id_list[[5]] else NA
  coeffs <- naturalCoef(mod)
  res <- rbind(list(Country=Country, flavor=flavor, energy=energy, model=model, nest=nest))
  res <- cbind(res, coeffs)
  return(res)
}) %>% do.call(plyr::rbind.fill, .)
@

<<Fitted_and_Residuals>>=
fitted_and_resid_data <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), f = function(mod, id){
  df <- select(mod$data, Year, iGDP, Country)
  # Trim fitted to be same length as df to eliminate problems with possible NAs at end of fitted
  df$fitted <- yhat(mod)[c(1:length(df$Year))]
  df$Residuals <- resid(mod)[c(1:length(df$Year))]
  # Parse the id to find out whether this is quality-adjusted data
  id_list <- strsplit(id, split = "[.]")[[1]]
  if (id_list[[2]] == "unadjusted"){
    df$flavor <- "Unadjusted"
  } else if (id_list[[2]] == "adjusted"){
    df$flavor <- "Quality-adjusted"
  } else {
    stop("Unknown adjustment.")
  }
  if (id_list[[3]] == "noE"){
    df$energy <- "Without energy"
  } else if (id_list[[3]] == "withE"){
    df$energy <- "With energy"
  } else {
    stop("Unknown energy.")
  }
  df$model <- id_list[[4]]
  df$nest <- if (length(id_list) > 4) id_list[[5]] else NA
  return(df)  
}) %>% do.call(rbind, .)
